Efficient Data Provenance Analysis for Concurrent Programs

### 2014-03-20 paper.tex
commtting to merge

\section{Introduction}
Multi-threaded programming is challenging.  In contrast to sequential
reasoning, multi-threaded programs require complex reasoning about many threads
of control and their interactions.  In shared memory programs, threads interact
by reading and writing memory locations.  Threads' reads and writes interleave
arbitrarily and nondeterministically. Each interleaving can lead to different
behaviors and memory states, some of which may be undesirable, like crashes or
data corruption.  Moreover, because complete concurrency testing is infeasiable
in general, undesirable interleavings can evade testing and lead to production
failures.

@@

A closely related recent effort in this space is Octet~\cite{octet} that
captures inter-thread communication soundly and, like \ctraps, can be used to
build dynamic concurrency analyses.  Octet differs from \ctraps in that it is
sound and was built to support analyses on Java programs.  Additionally, Octet
tracks the ``locality state'' of memory locations, rather than the last writer
slice information.  Octet's average run time overhead (26\%) is comparable to
the overhead of both last writer slicing and \ctraps and all three techniques
have low enough overheads in many cases for production use.

>>>>

\section{Introduction}
Multi-threaded programming is challenging.  In contrast to simple sequential
reasoning, multi-threaded programs require complex reasoning about many threads
of control and their interactions.  In shared memory programs, threads interact
by reading and writing memory locations.  Threads' reads and writes interleave
arbitrarily and nondeterministically. Each interleaving can lead to different
behaviors and memory states, some of which may be undesirable, like crashes or
data corruption.  Moreover, because complete concurrency testing is infeasiable
in general, undesirable interleavings can evade testing and lead to production
failures.

@@

A closely related recent effort on dynamic dependence analysis is
Octet~\cite{octet}, which captures inter-thread communication soundly and to
aid in building arbitrary concurrency analyses. Octet tracks the ``locality
state'' of memory locations to make dependence tracking efficient.   Octet
differs from \ctraps in that it focuses on soundness, was built primarily to
optimize dependence tracking, and does not discuss direct use of
dependence information to help with debugging.  Octet's average run time
overhead (26\%) is comparable to the overhead of both last writer slicing and
\ctraps and Octet, last writer slicing, and \ctraps all have low enough
overheads for production use in many cases.
